---
title: "Welcome to the REDCap Workshop!"
format: html
editor: visual
---

## Quarto

Quarto (the successor of **R Markdown**) enables you to weave together *human-readable content* and *executable code* in a single document. We will use Posit Cloud to work with Quarto documents that contain exercises for the session.

## Running Code

When you click the **green triangle** on the top right of the **code chunk**, the code gets run, and the result (if any) will appear underneath.

Here is a code chunk that asks R to calculate the sum of `1 + 1`. Go ahead and run it!

```{r}
1 + 1
```

The following code chunk will connect to a REDCap database and download its data into an object called `my_redcap_data`. Run the code chunk.

```{r}
library(REDCapR)

creds <- retrieve_credential_local("../data-private/credentials.csv", 1)

uri <- creds$uri
token <- creds$token

## TODO: Right now this has lots of empty rows. Come up with a better solution. Maybe download from a different, simpler database?
my_redcap_data <- redcap_read_oneshot(redcap_uri, token, forms = "demographics")$data
```
