---
title: "01a_redcapr"
format: html
editor: visual
---

## Extracting Data from REDCap using REDCapR

For the first 10 min, we will download REDCap data using [REDCapR](https://ouhscbbmc.github.io/REDCapR).

### Install latest version of REDCapR

Let's install with the newest version of REDCapR from GitHub.

```{r}
if (packageVersion("REDCapR") < "1.1.9005") {
  install.packages("remotes")
  remotes::install_github("OuhscBbmc/REDCapR")
}
```

### Retrieve Secure Token

We'll discuss tokens in more depth at the end of the workshop. For now, know that a "token" is a secret value that serves as your personal password to a specific REDCap project.

```{r}
# path_credential <- "../data-private/credentials.csv"
path_credential <- "redcapcon_2023_redcap_r_workshop/data-private/credentials.csv"
credential  <- REDCapR::retrieve_credential_local(path_credential, 1L)
credential
```

### Peek at Variables, Events, & Instruments

Here's a project of fake data that Stephan created to mimic the CAR-T investigation. The first snippet reveals info from the 368 variables.\
The second reveals info about the combinations of events & instruments.

```{r}
REDCapR::redcap_metadata_read(
  redcap_uri  = credential$redcap_uri,
  token       = credential$token
)$data

REDCapR::redcap_event_instruments(
  redcap_uri  = credential$redcap_uri,
  token       = credential$token
)$data
```

If important details are obscured, use `View()` to see things in a nice scrollable table inside RStudio:

\`\`\`r View(REDCapR::redcap_metadata_read( redcap_uri = credential$redcap_uri,  token = credential$token )\$data)
