---
title: "Welcome to the REDCap Workshop!"
format: html
editor: visual
---

## Quarto

Quarto (the successor of **R Markdown**) enables you to weave together *human-readable content* and *executable code* in a single document. We will use Posit Cloud to work with Quarto documents that contain exercises for the session.

## Running Code

In Quarto, executable code is embedded as **code chunks**. They appear with a gray background, like so:

```{r}
# I'm a code chunk!
```

When you click the **green triangle** on the top right of the **code chunk**, the code gets run, and the result (if any) will appear underneath.

Here is a code chunk that asks R to calculate the sum of `1 + 1`. Go ahead and run it!

```{r}
1 + 1
```

The following code chunk will use the **REDCapR** package to connect to a REDCap database and download its data into an object called `my_redcap_data`. Run the code chunk.

```{r}
library(REDCapR)

creds <- retrieve_credential_local("../data-private/credentials.csv", 1)

uri <- creds$redcap_uri
token <- creds$token

my_redcap_data <- redcap_read_oneshot(uri, token)$data
```

When this runs successfully, it will give you a message that [looks like an error]{style="color:red"} but is really just a status message. The HTTP status code "200" means "success."

So if this ran without an error, pat yourself on the back! You just used R to access the REDCap API via REDCapR and downloaded a project. Pretty cool!
